Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-17 nir_companions.tex
fix precent space

At this point one would normally combine all the optimally extracted nod spectra together to improve the signal-to.noise. {However, we discovered extended artefacts in the optimally reduced nod spectra. We were not able to identify why these artefacts are large and extended but they occur near the presence of a large cosmic rays or bad pixel spike seen in the rectangular extraction. These artefacts were not observed in previous works using this pipeline in the \textit{H}-band, so there may be a wavelength dependent affect. The variance weighting procedure during the optimal extraction is somehow being heavily affected by these spikes.} An example of this can be seen in Fig.~\ref{fig:nod_artefacts} where a spike in the rectangular extraction corresponds to the large extended features in the optimal extraction. The amplitude of these artefacts created flux deviations in the combined optimally extracted spectra up to \(\sim\)0.5 per cent.
Therefore, we took measures to remove these artefacts before combining the nod spectra as we are trying to recover companion spectra with expected flux ratios \(\rm {F_2}/{F_1} < 1\)per cent. {Parameters of the pipeline were adjusted to try and remove these artefacts, such as the $\sigma$ rejection limits and the aperture width with limited success. In a small number of instances allowing the aperture width to be automatically adjusted removed the artefacts.}

>>>>

At this point one would normally combine all the optimally extracted nod spectra together to improve the signal-to.noise. {However, we discovered extended artefacts in the optimally reduced nod spectra. We were not able to identify why these artefacts are large and extended but they occur near the presence of a large cosmic rays or bad pixel spike seen in the rectangular extraction. These artefacts were not observed in previous works using this pipeline in the \textit{H}-band, so there may be a wavelength dependent affect. The variance weighting procedure during the optimal extraction is somehow being heavily affected by these spikes.} An example of this can be seen in Fig.~\ref{fig:nod_artefacts} where a spike in the rectangular extraction corresponds to the large extended features in the optimal extraction. The amplitude of these artefacts created flux deviations in the combined optimally extracted spectra up to \(\sim\)0.5 per cent.
Therefore, we took measures to remove these artefacts before combining the nod spectra as we are trying to recover companion spectra with expected flux ratios \(\rm {F_2}/{F_1} < 1\) per cent. {Parameters of the pipeline were adjusted to try and remove these artefacts, such as the $\sigma$ rejection limits and the aperture width with limited success. In a small number of instances allowing the aperture width to be automatically adjusted removed the artefacts.}
